### 2020-12-04 sections/expertise.tex
Update expertise.tex

\cvskill
{Interests}
{Cabinets composition and allocation, ministerial turnover, political elites socialisation, civil service}

\cvskill
{}
{systems, political participation, digital media, electronic government}\\

\cvskill
{Techniques} 
{Survival analysis, regression modelling, multilevel models, factor analysis, spatial analysis, social}

\cvskill
{} 
{network analysis, qualitative comparative analysis, topic modelling} \\

>>>>

\cvskill
{Main Interests}
{Cabinets composition and allocation, ministerial turnover, presidential systems, political elites, }

\cvskill
{}
{civil service systems, crisis management}\\

\cvskill
{Techniques} 
{Survival analysis and competing risks models, propensity score methods, multilevel models, }

\cvskill
{} 
{spatial analysis, social network analysis, qualitative comparative analysis} \\
